Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2017-04-11 cbm-rbd-paper.tex
work on revision sec 3&4

As a running example, we consider a simplified automotive braking system
consisting of four component types $M$, $H$, $C$ and $P$,
with reliability block diagram as depicted in Figure~\ref{fig:brakesys-layout}.
The master brake cylinder ($M$) activates all four wheel brake cylinders ($C_1$ -- $C_4$),
which in turn actuate a braking pad assembly each ($P_1$ -- $P_4$).
The hand brake mechanism ($H$) directly actuates the brake pad assemblies $P_3$ and $P_4$;
the vehicle brakes when at least one brake pad assembly is actuated.
Note that because of the `handbrake shortcut', this system cannot be described as a nesting of series and parallel subsystems.
%This system is observed until time $\tnow$,
%leading to censored observation of certain component lifetimes within the system.

@@

Continuing our example,
the survival signature for the system in Figure~\ref{fig:brakesys-layout} is given in Table~\ref{tab:brakesys-survsign},
omitting the entries for which $\Phi(l_M, l_H, l_C, l_P) = 0$ or $\Phi(l_M, l_H, l_C, l_P) = 1$,
because the full table would contain $\prod_{k=1}^K (N_k + 1) = 2 \times 2 \times 5 \times 5 = 100$ rows.
***The omitted rows from Table~\ref{tab:brakesys-survsign} can be determined as follows:
\begin{itemize}
\item Take a row, decrease $l_k$ for one $k \in \{M, H, C, P\}$ by 1.
If the resulting row is not in Table~\ref{tab:brakesys-survsign}, then the corresponding $\Phi$ is $0$.
\item Take a row, increase $l_k$ for one $k \in \{M, H, C, P\}$ by 1.
If the resulting row is not in Table~\ref{tab:brakesys-survsign}, then the corresponding $\Phi$ is $1$.
\end{itemize} 
The \textsf{R} package \texttt{ReliabilityTheory} \citep{2016:aslett-RT}
provides a convenient function to calculate the survival signature table based on a given graph.
***To illustrate how the table entries are generated,
consider the case $l_M = 0, l_H = 1, l_C = 0, l_P = 1$,
i.e., $M$ has failed, $H$ functions, $C_1$ -- $C_4$ have failed, and one of $P_1$ -- $P_4$ functions.
The system functions only if the single functioning type $P$ component is either $P_3$ or $P_4$.
As the type $P$ components are exchangeable, each of $P_1$ -- $P_4$ has the same probability of being the functioning component,
and so the probability of $P_3$ or $P_4$ being the functioning component is $2 / 4$, thus $\Phi(0, 1, 0, 1) = 0.5$.

@@

We consider the well-known Weibull model for component lifetimes,
which is used in a wide variety of reliability studies. 
To keep things simple, we assume that the shape parameter of the Weibull distribution is known,
and that only the scale parameter needs to be estimated.
The model could be extended to learn also the shape parameter in a later step,
using, e.g., the discretized approach by \cite{1969:soland}.

By using a Bayesian approach, described in Section~\ref{sec:weibull},
our component model allows to include both expert assessments and test data (if available),
and furthermore can account for component lifetime information from the current operational cycle up to $\tnow$.
%***component model: weibull with fixed shape,
%inverse gamma prior on scale parameter,
%fix priors via expected lifetime and prior strength,
%test data inclusion
%with noninformatiove right-censoring
%
In Section~\ref{sec:postpred} we derive the posterior predictive distribution
for the Weibull component model as needed for the current system reliability calculation.
Finally, in Section~\ref{sec:sysreltnow}, we adapt the method from Section~\ref{sec:sysrel} for the adaptive setting,
resulting in a formula for $\Rsysnow(t)$.
%***output is $\Rsysnow(t)$, the current (at time $\tnow$) system reliability function
%(residual life distribution, RLD)
%taking into account the current system state,
%including the current ages of system components, 
%and the lifetime histories of all component types,
%including test data (if available) and expert assessments.

The model description below follows closely \cite[\S 2, \S 4.1 -- \S 4.3]{2016:walter-coolen},
who presented the same residual life distribution model.
However, \cite{2016:walter-coolen} did not consider maintenance policies,
but focus instead on a generalization of the RLD model by using imprecise probability models*** for the component models.
%These sets of priors can be seen as parametric P-boxes,
%a certain kind of imprecise probability model \citep[see, e.g.,][]{itip}.
%Such models allow for vague and partial prior specifications,
%and provide sensitivity to prior-data conflict \cite[\S 2.2.3.3]{diss}.

@@

\subsection{Component posterior predictive distributions at $\tnow$}
\label{sec:postpred}

@@

Following our comments at the end of Section~\ref{sec:weibull},
the component models can be further updated
using information gained from the current run of the system until $\tnow$:
Any failure times of failed components,
and the right-censoring time $\tpnow$ for each non-failed component,
can be used to update $\nkz$ and $\ykz$ according to \eqref{eq:ig-update}.
We denote the resulting parameter values by $\nknow$ and $\yknow$.
%(It is of course possible to update $\nkz$ and $\ykz$ directly to $\nknow$ and $\yknow$ if no test data is available.)
%Furthermore, the fact that the components in the system that still function have reached the age $\tnow$
%must be used when calculating the posterior predictive distribution.

@@

where $\eknow$ is the number of components that have failed by $\tnow$,
and $\cknow$ is the number of components that have not failed by $\tnow$.

@@

\subsection{Conditional system reliability function at $\tnow$}
\label{sec:sysreltnow}

Now that we can calulate the component posterior predictive distributions at $\tnow$,
we can use the method from Section~\ref{sec:sysrel}
to determine the system residual life distribution (RLD) $\Rsysnow(t)$,
giving us the probability that the system functions at times $t > \tnow$,
taking into account all information available at $\tnow$:
\begin{align}
\Rsysnow(t) &= \sum_{l_1=0}^{c_1^{(\tnow)}} \cdots \sum_{l_K=0}^{c_K^{(\tnow)}} \Phinow(l_1,\ldots,l_K)
               \prod_{k=1}^K P(C^k_t = l_k\mid\nkz,\ykz, \vectknow)\,.
\label{eq:sysrel-tnow}
\end{align}
Since this is the distribution of system reliability conditional on the system surviving until $\tnow$,
we have that $\Rsysnow(\tnow) = 1$ for any $\tnow$.
Note that if one or several components have failed by $\tnow$,
the system reliability block diagram changes, and with it the survival signature $\Phi(l_1,\ldots,l_K)$.
We denote the current survival signature by $\Phinow(l_1,\ldots,l_K)$.

>>>>

As a running example, we consider a simplified automotive braking system
consisting of four component types $M$, $H$, $C$ and $P$,
with the reliability block diagram as depicted in Figure~\ref{fig:brakesys-layout}.
The master brake cylinder ($M$) activates all four wheel brake cylinders ($C_1$ -- $C_4$),
which in turn actuate a braking pad assembly each ($P_1$ -- $P_4$).
The hand brake mechanism ($H$) directly actuates the brake pad assemblies $P_3$ and $P_4$;
the vehicle brakes when at least one brake pad assembly is actuated.
Note that because of the `handbrake shortcut', this system cannot be described as a nesting of series and parallel subsystems.
%This system is observed until time $\tnow$,
%leading to censored observation of certain component lifetimes within the system.

@@

Continuing our example,
the survival signature for the system in Figure~\ref{fig:brakesys-layout} is given in Table~\ref{tab:brakesys-survsign},
omitting the entries for which $\Phi(l_M, l_H, l_C, l_P) = 0$ or $\Phi(l_M, l_H, l_C, l_P) = 1$,
since the full table would contain $\prod_{k=1}^K (N_k + 1) = 2 \times 2 \times 5 \times 5 = 100$ rows.
%
To illustrate how the table entries are obtained,
consider the case $l_M = 0, l_H = 1, l_C = 0, l_P = 1$,
i.e., $M$ has failed, $H$ functions, $C_1$ -- $C_4$ have failed, and one of $P_1$ -- $P_4$ functions.
The system functions only if the single functioning type $P$ component is either $P_3$ or $P_4$.
As the type $P$ components are exchangeable, each of $P_1$ -- $P_4$ has the same probability of being the functioning component,
and so the probability of $P_3$ or $P_4$ being the functioning component is $2 / 4$, thus $\Phi(0, 1, 0, 1) = 0.5$.
%
The omitted rows from Table~\ref{tab:brakesys-survsign} can be determined as follows:
\begin{itemize}
\item Take a row, decrease $l_k$ for one $k \in \{M, H, C, P\}$ by 1.
If the resulting row is not in Table~\ref{tab:brakesys-survsign}, then the corresponding value of $\Phi$ is $0$.
\item Take a row, increase $l_k$ for one $k \in \{M, H, C, P\}$ by 1.
If the resulting row is not in Table~\ref{tab:brakesys-survsign}, then the corresponding value of $\Phi$ is $1$.
\end{itemize} 
The \textsf{R} package \texttt{ReliabilityTheory} \citep{2016:aslett-RT}
provides a convenient function to calculate the survival signature table based on any given graph.

@@

We consider the well-known Weibull model for the component lifetimes,
which is used in a wide variety of reliability studies. 
To keep things simple, we assume that the shape parameter of the Weibull distribution is known,
and that only the scale parameter needs to be estimated.
The model could be extended to learn also the shape parameter in a later step,
using, e.g., the discretized approach by \cite{1969:soland}.

By using the Bayesian approach described in Section~\ref{sec:weibull},
our component model allows to include both expert assessments and test data (if available),
and furthermore can account for component lifetime information from the current operational cycle up to $\tnow$.
%***component model: weibull with fixed shape,
%inverse gamma prior on scale parameter,
%fix priors via expected lifetime and prior strength,
%test data inclusion
%with noninformatiove right-censoring
%
In Section~\ref{sec:postpred} we derive the posterior predictive distribution
for the Weibull component model as needed for the current system reliability calculation.
Finally, in Section~\ref{sec:sysreltnow}, we adapt the method from Section~\ref{sec:sysrel} for the adaptive setting,
resulting in a formula for $\Rsysnow(t)$.
%***output is $\Rsysnow(t)$, the current (at time $\tnow$) system reliability function
%(residual life distribution, RLD)
%taking into account the current system state,
%including the current ages of system components, 
%and the lifetime histories of all component types,
%including test data (if available) and expert assessments.

The model description below follows closely \cite[\S 2, \S 4.1 -- \S 4.3]{2016:walter-coolen},
who presented the same residual life distribution model.
However, \cite{2016:walter-coolen} do not consider maintenance policies,
but focus instead on a generalization of the RLD model by using imprecise probability models for the component lifetimes.
%These sets of priors can be seen as parametric P-boxes,
%a certain kind of imprecise probability model \citep[see, e.g.,][]{itip}.
%Such models allow for vague and partial prior specifications,
%and provide sensitivity to prior-data conflict \cite[\S 2.2.3.3]{diss}.

@@

\subsection{Component posterior predictive distributions determined at $\tnow$}
\label{sec:postpred}

@@

Following our comments at the end of Section~\ref{sec:weibull},
the component models can be further updated
using information gained from the current operational cycle as of $\tnow$: %run of the system until $\tnow$:
failure times of failed components,
and the right-censoring time $\tpnow$ for each non-failed component,
can be used to update $\nkz$ and $\ykz$ according to \eqref{eq:ig-update}.
We denote the resulting parameter values by $\nknow$ and $\yknow$.
%(It is of course possible to update $\nkz$ and $\ykz$ directly to $\nknow$ and $\yknow$ if no test data is available.)
%Furthermore, the fact that the components in the system that still function have reached the age $\tnow$
%must be used when calculating the posterior predictive distribution.

@@

where $\eknow$ denotes the number of type $k$ components that have failed by $\tnow$ during the current operational cycle,
and $\cknow$ denotes the number of type $k$ components that have not failed by $\tnow$ during the current operational cycle.

@@

\subsection{Conditional system reliability function determined at $\tnow$}
\label{sec:sysreltnow}

Now that we can calulate the component posterior predictive distributions at $\tnow$,
we can use the method from Section~\ref{sec:sysrel}
to determine the system residual life distribution (RLD) $\Rsysnow(t)$,
giving us the probability that the system functions at times $t > \tnow$,
taking into account all information available at $\tnow$:
\begin{align}
\Rsysnow(t) &= \sum_{l_1=0}^{c_1^{(\tnow)}} \cdots \sum_{l_K=0}^{c_K^{(\tnow)}} \Phinow(l_1,\ldots,l_K)
               \prod_{k=1}^K P(C^k_t = l_k\mid\nkz,\ykz, \vectknow)\,.
\label{eq:sysrel-tnow}
\end{align}
Since this is the distribution of system reliability conditional on the system surviving until $\tnow$,
we have that $\Rsysnow(\tnow) = 1$ for any $\tnow$ before system failure.
Note that if one or several components have failed by $\tnow$,
the system reliability block diagram changes, and with it the survival signature $\Phi(l_1,\ldots,l_K)$.
We denote the current survival signature by $\Phinow(l_1,\ldots,l_K)$.
